Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
Separate multiple people
Separate information

>>>>

# Separate information about people
stop_df<- stop_df %>%
    filter(nchar(Dispositions) == 6) %>%
      mutate(Race = substr(Dispositions,1,1)) %>%
        mutate(Gender = substr (Dispositions,2,2)) %>%
          mutate(AgeRange = substr (Dispositions,3,3)) %>%
            mutate(Reason =substr(Dispositions,4,4)) %>%
              mutate(Enforcement = substr(Dispositions,5,5)) %>%
                 mutate(CarSearch = substr(Dispositions,6,6))
